_preset Default
ai_aim_max_angle 0.7854
ai_aim_min_angle 0.19635
ai_aim_min_speed 0.24
ai_aim_predict_time 0.4
ai_aim_use_smooth_aim 1
ai_die_in_anomaly 0
ai_use_old_vision 0
ai_use_torch_dynamic_lights on
default_controls
bind left kLEFT
bind right kRIGHT
bind up kUP
bind down kDOWN
bind jump kSPACE
bind crouch kLCONTROL
bind accel kLSHIFT
bind sprint_toggle kX
bind forward kW
bind back kS
bind lstrafe kA
bind rstrafe kD
bind llookout kQ
bind rlookout kE
bind cam_zoom_in kT
bind cam_zoom_out kSUBTRACT
bind torch kL
bind night_vision kN
bind show_detector kO
bind wpn_1 k1
bind wpn_2 k2
bind wpn_3 k3
bind wpn_4 k4
bind wpn_5 k5
bind wpn_6 k6
bind wpn_next kY
bind wpn_fire mouse1
bind wpn_zoom mouse2
bind wpn_reload kR
bind wpn_func kV
bind wpn_firemode_prev k9
bind wpn_firemode_next k0
bind pause kPAUSE
bind drop kG
bind use kF
bind screenshot kF12
bind quit kESCAPE
bind console kGRAVE
bind inventory kTAB
bind buy_menu kB
bind active_jobs kC
bind quick_use_1 kF1
bind quick_use_2 kF2
bind quick_use_3 kF3
bind quick_use_4 kF4
bind quick_save kF5
bind quick_load kF9
bind custom1 kNUMPAD1
bind custom2 kNUMPAD2
bind custom3 kNUMPAD3
bind custom4 kNUMPAD4
bind custom5 kNUMPAD5
bind custom6 kNUMPAD0
bind custom12 kZ
bind custom13 k7
bind custom14 k8
bind custom15 kU
cam_inert 0.
cam_slide_inert 0.25
cl_cod_pickup_mode 1
cl_dynamiccrosshair on
con_sensitive 0.15
discord_status 1
discord_update_rate 0.5
fov 76.
g_autopickup on
g_backrun on
g_crouch_toggle on
g_dynamic_music off
g_firepos off
g_game_difficulty gd_veteran
g_god off
g_hit_pwr_modif 1.5
g_important_save on
g_multi_item_pickup on
g_sleep_time 24
g_unlimitedammo off
g_use_tracers on
hud_crosshair on
hud_crosshair_dist off
hud_draw on
hud_fov 0.6
hud_info on
hud_weapon on
keypress_on_start 1
log_missing_ini off
mouse_invert off
mouse_sens 0.12
ph_frequency 100.00000
ph_gravity 19.62
ph_iterations 18
power_loss_bias 0.1
power_loss_factor 0.5
r1_detail_textures off
r1_dlights on
r1_dlights_clip 40.
r1_fog_luminance 1.1
r1_glows_per_frame 16
r1_lmodel_lerp 0.1
r1_pps_u 0.
r1_pps_v 0.
r1_software_skinning 0
r1_ssa_lod_a 64.
r1_ssa_lod_b 48.
r1_tf_mipbias 0.
r2_aa off
r2_aa_break (0.800000, 0.100000, 0.000000)
r2_aa_kernel 0.5
r2_aa_weight (0.250000, 0.250000, 0.000000)
r2_allow_r1_lights off
r2_detail_bump on
r2_dof -1.250000,1.400000,600.000000
r2_dof_enable off
r2_dof_kernel 5.
r2_dof_sky 30.
r2_drops_control (0.000000, 0.000000, 0.000000)
r2_exp_donttest_shad off
r2_fxaa 0
r2_gloss_factor 2.5
r2_gloss_min 0.5
r2_ls_bloom_fast off
r2_ls_bloom_kernel_b 0.1
r2_ls_bloom_kernel_g 1.
r2_ls_bloom_kernel_scale 0.05
r2_ls_bloom_speed 100.
r2_ls_bloom_threshold 0.
r2_ls_depth_bias -0.0003
r2_ls_depth_scale 1.00001
r2_ls_dsm_kernel 0.7
r2_ls_psm_kernel 0.7
r2_ls_squality 1.
r2_ls_ssm_kernel 0.7
r2_lut off
r2_lut_texture 1
r2_mask_control (0.000000, 0.000000, 0.000000)
r2_mblur 0.
r2_mblur_enable off
r2_parallax_h 0.02
r2_slight_fade 0.5
r2_soft_particles on
r2_soft_water on
r2_ss_sunshafts_length 1.
r2_ss_sunshafts_radius 1.
r2_ssa_lod_a 64.
r2_ssa_lod_b 48.
r2_ssao st_opt_high
r2_ssao_blur off
r2_ssao_half_data off
r2_ssao_hbao off
r2_ssao_hdao on
r2_ssao_mode hdao
r2_ssao_opt_data off
r2_steep_parallax on
r2_sun on
r2_sun_depth_far_bias -0.00002
r2_sun_depth_far_scale 1.
r2_sun_depth_near_bias 0.00001
r2_sun_depth_near_scale 1.
r2_sun_details off
r2_sun_far 180.
r2_sun_focus on
r2_sun_lumscale 1.5
r2_sun_lumscale_amb 1.
r2_sun_lumscale_hemi 1.
r2_sun_near 20.
r2_sun_near_border 0.75
r2_sun_quality st_opt_medium
r2_sun_shafts st_opt_medium
r2_sun_shafts_min 0.
r2_sun_shafts_value 0.75
r2_sun_tsm on
r2_sun_tsm_bias -0.01
r2_sun_tsm_proj 0.3
r2_sunshafts_mode volumetric
r2_tf_mipbias 0.
r2_tnmp_a 0.15
r2_tnmp_b 0.5
r2_tnmp_c 0.1
r2_tnmp_d 0.2
r2_tnmp_e 0.2
r2_tnmp_exposure 0.16033
r2_tnmp_f 0.3
r2_tnmp_gamma 0.76667
r2_tnmp_onoff 0.
r2_tnmp_w 1.12
r2_tonemap on
r2_tonemap_adaptation 10.
r2_tonemap_amount 1.
r2_tonemap_lowlum 0.5
r2_tonemap_middlegray 1.5
r2_volumetric_lights on
r2_wait_sleep 0
r2_water_reflections on
r2_zfill off
r2_zfill_depth 0.25
r2em 0.
r3_dynamic_wet_surfaces on
r3_dynamic_wet_surfaces_far 30.
r3_dynamic_wet_surfaces_near 10.
r3_dynamic_wet_surfaces_sm_res 256
r3_gbuffer_opt on
r3_minmax_sm off
r3_msaa st_opt_off
r3_msaa_alphatest st_opt_off
r3_use_dx10_1 off
r3_volumetric_smoke on
r4_enable_tessellation on
r4_wireframe off
r__actor_shadow off
r__clear_models_on_unload 0
r__detail_density 0.6
r__detail_height 1.
r__detail_radius 49
r__dtex_range 50.
r__enable_grass_shadow 0
r__geometry_lod 0.75
r__no_scale_on_fade 0
r__optimize_dynamic_geom 1
r__optimize_shadow_geom 1
r__optimize_static_geom 1
r__supersample 1
r__tf_aniso 8
r__use_precompiled_shaders 0
r__wallmark_ttl 50.
renderer renderer_r2.5
rs_borderless 1
rs_c_brightness 1.
rs_c_contrast 1.
rs_c_gamma 1.
rs_cam_pos off
rs_fullscreen off
rs_refresh_60hz on
rs_skeleton_update 32
rs_stats off
rs_v_sync on
rs_vis_distance 1.
slot_0 medkit
slot_1 bandage
slot_2 medkit_army
slot_3 stimpack
snd_acceleration on
snd_cache_size 32
snd_device Generic Software
snd_efx off
snd_targets 32
snd_volume_eff 0.4
snd_volume_music 0.
texture_lod 1
time_factor 1.000000
vid_mode 1366x768
wpn_aim_toggle 1
wpn_degradation 0.75
